\TITLE

### 2023-06-15 paper/main.tex
prepare for IJIS journal

@@

Providing personal information exposes users to privacy risks, i.e. potential loss of control over personal information~\cite{smithInformationPrivacyResearch2011}.

Such personal information can be used deliberately or accidently (e.g., by theft) 
for insider disclosure, unauthorized access, or commercial gains. For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals. 
In turn, it can lead to an unintentional violation of the GDPR or CCPA, profiled advertisements or even criminal activities like identity theft or illegal tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.

@@

The contribution of our paper is:
\begin{itemize}
\item proposing a novel protocol that:
  \begin{itemize}
  \item allows \textbf{anonymous} service provision, i.e., the service provider does not need to collect any personal information from the customer.
  \item achieves \textbf{fairness} by carefully designing the protocol as an interactive non-cooperative game, in which the SP remains in an advantageous position and the customer in a disadvantageous position with an option to start a dispute in case a misbehaviour of SP.
  \item \textbf{does not rely on centralized TTP}, but uses decentralized blockchain and distributed content-addressable storage network.
  \item In conflict-free transactions does not require customers to interact with the blockchain, achieving better \textbf{user-experience and practicality}.
  \item allows the \textbf{delivery of physical materials}, which was rarely addressed by other researchers or based on strong and unpractical assumptions.
  \item guarantees the \textbf{remote availability of the results}, even in case of the SP denial of service.
  \end{itemize} 
\item Systemise often misused definitions of anonymity, pseudonymity, linkability, and traceability.
\item Proposing a framework for analyzing fairness in fair-exchange protocols.
\item Discuss the possible improvements to the protocol with the use of secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution techniques.
\end{itemize}

@@

To our best knowledge, the first system that allowed for fair exchange of physical products was proposed by Zhang et al. in 2006~\cite{zhangPracticalFairExchangeEPayment2006}. The protocol uses buyer's bank as TTP, and assumes no coalition between parties to achieve anonymity. 
Authors of

Authors of~\cite{mohammedalarajFairnessPhysicalProducts2012} proposed an protocol for fair-exchage involving physical materials delivery. The protocol assumes the existence of an offline~\footnote{\textit{Offline} (also called \textit{optimistic}) TTP compared to \textit{online} TTP is in improvement which assumes the TTP being involved only in the case of a dispute between parties~\cite{rayFairExchangeEcommerce2002}.} TTP that is involved only in the event of a dispute. The protocol works as follows: 
\begin{enumerate}
\item The buyer sends an encrypted payment to the seller along with the proof of validity.
\item The seller validates the proof, which convinces him that the decrypted payment will also be valid.
\item The seller forwards the physical product to the trusted delivery agent (DA).
\item The buyer verifies whether the product is the one he ordered.
\item The buyer creates a proof of delivery and sends it along with the decryption key to the seller.
\end{enumerate}

@@

\begin{enumerate}
    \item The buyer buys a digital coin from his bank, blind signature is used to preserve customer's privacy.
    \item The buyer sends to the seller the purchase details, address of DC, customer's bank signature, and some meta data to preserve the integrity of transaction, communication is done over Tor.
    \item The seller request a redemption of the digital coin.
    \item The seller posts the product to the DC via delivery serivice.
    \item The DA collects the product from the SC and posts it to the DC.
    \item The buyer collects the product from the DC using a password.
    \item The buyer checks if the product is the ordered one, if not, opens a dispute to TTP.
\end{enumerate}

@@

The protocol works as follows:
\begin{enumerate}
    \item Alice and Bob generate a 2-of-2 threshold escrow account using Thresh-Key-Gen protocol and send funds to it.
    \item Alice and Bob split their secret keys into \(n=2t+1\) secret shares using Shamir Secret Shamir protocol, where \(n\) is the number of mediators that participate in the decentralized network and \(t+1\) becomes the threshold of a sufficient number of mediators to reconstruct the secret key.
    \item Alice and Bob encrypt each \textit{i}-th key share using public key of \textit{i}-th mediator.
    \item Alice and Bob exchange the sets of encrypted key shares with each other and send funds to the escrow account.
\end{enumerate}

@@

Meng et al., 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol by the crowdsourced dispute resolution system. However, it does not take anonymity into consideration.

Bîrjoveanu, 2022~\cite{birjoveanuTwoPartyECommerceProtocols2022} is the closest to our protocol, however, it is based on strong assumptions, namely, existence of TTP, banks supporting confidental transactions with commit buffers, and mantainng a global list of coins' serial numbers.

@@

\ifdefstring{\FORMAT}{\DOUBLECOLUMN}{\begin{table*}}{\begin{table}}
\centering
\newcommand{\YES}{\cellcolor{green!50}Yes}
\newcommand{\YESBUT}{\cellcolor{green!25}Yes*}
\newcommand{\ID}{\cellcolor{green!25}Identity}
\newcommand{\PSEUDO}{\cellcolor{green!35}Pseudonym}
\newcommand{\ANON}{\cellcolor{green!50}Anonymity}
\newcommand{\NO}{\cellcolor{red!50}No}
\newcommand{\TTP}{\cellcolor{red!50}TTP}
\newcommand{\BC}{\cellcolor{green!50}BC}
\newcommand{\BCBUT}{\cellcolor{green!35}BC*}
\caption{Comparision of related works.}
\label{tab:comparision}
\setlength{\tabcolsep}{3pt}

\ifdefstring{\FORMAT}{\DOUBLECOLUMN}{\begin{tabular}{|c|c|c|c|c|c|}}{\begin{tabular}{|c|c|c|c|c|c|}}

\hline
Protocol & Fair \newline exchange & Anonymity & Dispute resolution & Trust & Physical \newline delivery \\
\hline
\cite{zhangPracticalFairExchangeEPayment2006} (2006) & \YES & \YESBUT & \YES & \TTP & \YES \\
\hline
\cite{mohammedalarajFairnessPhysicalProducts2012} (2012) & \YESBUT & \NO & \YES & \TTP & \YES \\
\hline
Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} (2017) & \YES & \PSEUDO & \NO & \BC & \YES \\
\hline
\cite{hinarejosSolutionSecureCertified2019} (2019) & \YES & \NO & \NO & \BC & \NO \\
\hline
Themis~\cite{mengThemisDecentralizedEscrow2019} (2019) & \YES & \NO & \YES & \BC & \NO \\
\hline
PPPDCP~\cite{birjoveanuTwoPartyECommerceProtocols2022} (2022) & \YES & \YES & \YES & \TTP & \YES \\
\hline
This paper & \YES & \YES & \YES & \BCBUT & \YES \\
\hline

@@

\ifdefstring{\FORMAT}{\DOUBLECOLUMN}
{\end{table*}}
{\end{table}}

@@

\subsection{Physical products}\label{sec:physical-products}
The use cases we address in this paper use physical materials like blood, urine, hair, and other biological materials.
This requirement, combined with the requirement of anonymity, is a challenging part of the fair-exchange protocols. The problem arises when the seller wants to sent the product to the buyer who wants to remain anonymous. Most of the existing protocols either assume the existence of trusted delivery agent~\cite{mohammedalarajFairnessPhysicalProducts2012,birjoveanuAnonymityFairexchangeEcommerce2015}, or use complex delivery mechanism similar to onion rounting involving multiple many delivery services~\cite{altawyLelantosBlockchainBasedAnonymous2017}.

However, our use case is different in that the physical materials are transfered from the (anonymous) customer to the (public) SP. This, allows for siplification of the delivery process. We assume that there is a way to anonymously deliver a package without revealing the customer personal information either via SP's drop box, Parcel Locker services (e.g. Amazon Locker, InPost~\cite{inpostParcelLockerService}), a customer's trusted party, of even post office.

@@

\begin{figure}[h!]
\includegraphics[width=9cm]{anonymity-diagram.png}
\centering
\caption{Let us assume Alice to be the customer willing to keep her identity anonymous and Bob to be the public SP. Alice controls two addresses, 1 and 2; the connection between her real identity and the first address has been compromised, and therefore the identification is possible; the connection between the second pseudonym is still unknown and therefore anonymous. Alice takes two actions; the first one from the compromised address and the second one from the anonymous one. The first action is confidential; therefore, even though the pseudonym has been compromised, the action can not be associated with Alice. The second action is transparent; therefore, Alice maintains her anonymity as long as the connection to the second pseudonym is concealed.}

@@

\item $\mathrm{T}_\mathrm{issue}$ - time at which the $\mathrm{PoD}$ is issued.
\item
  $\mathrm{T}_\mathrm{pay}$ - deadline to pay for the transaction.
\item
  $\mathrm{T}_\mathrm{provide}$ - deadline to provide a result of the service.
\item $\mathrm{address}$ - payment address of the SP's anonymous blockchain account.
\item $\mathrm{provisionID}$ - the number uniquely identifying the transaction previously generated by the customer.
\item $\mathrm{pk(C)}$ - customer's public key used to encrypt the result published on the public storage network.
\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature guaranteeing non-repudiation.
\end{itemize}

@@

\begin{figure}[ht!]
\includegraphics[width=9cm]{anonser-protocol.png}
\centering
\caption{Messages exchanged in the protocol.}
\label{fig:protocol-diagram}
\end{figure}

@@

\begin{enumerate}
\item Both parties start from a neutral position $\neutral$.
\item After completing a transaction, both parties end up in advantaged positions (\plus{}). In other words, they have an intrinsic motivation to initialize and complete the transaction.
\item The protocol steps are atomic—there are no intermediate steps.
\item The protocol can go only forward—there is no way of reverting any action.
\item Repeating the first step starts a new transaction. Repeating any other step is considered abnormal and gets ignored. For example, paying for the invoice twice does not cause any effect on the curse of the protocol.
\item Once published, the result is available to the customer on the storage network. The idea of guaranteeing it cryptographically is discussed in Section~\ref{sec:discussion}.
\item Winning the dispute leads to a neutral position ($\neutral$).
\item Losing the dispute leads to a punishment greater than any reward, leading to a disadvantaged position (\minus{}). Hence, the rational customer will not start a dispute that he is unsure of winning.
\item Both the customer and the SP are rational (selfish). They always prefer to go from the worst position (\minus{} or $\neutral${}) to a better position ($\neutral$ or \plus), but also risk a temporary worst position in favor of a later better position if and only if at any time they can get out of the worst position; in particular, at any time the customer can start a dispute and, if the SP has misbehaved, get out of disadvantaged position (\minus) to the neutral position ($\neutral$).
\end{enumerate}

@@

\begin{figure}[h!]
\includegraphics[width=9cm]{model.png}
\centering
\caption{Positions after each step of protocol}
\label{fig:positions}
\end{figure}

@@

The Figure~\ref{fig:misbehaviour} shows the transitions of positions when the SP tries to misbehave and does not execute service after receiving the payment. The customer reacts by starting a dispute and the protocol ends up neutral to the customer and disadvantaged to the SP positions.

\begin{figure}[h!]
\includegraphics[width=9cm]{misbehaviour.png}
\centering
\caption{Transitions of positions where the SP is misbehaving and the customer starts a dispute}
\label{fig:misbehaviour}
\end{figure}
the rational path for both parties is to follow the protocol as shown in the Figure~\ref{fig:rational}.

\begin{figure}[h!]
\includegraphics[width=9cm]{rational.png}
\centering
\caption{Transitions of positions where both the customer and the SP are following the protocol}
\label{fig:rational}
\end{figure}

@@

\paragraph{Provable Results Availability}
Content addressable networks such as IPFS can not guarantee the availability of the content\footnote{Nothing prevents the SP from publishing the result, receiving the $\mathrm{cid}$, publishing $\mathrm{PoP}$, and immediately after removing the result from the local storage. In case of dispute, the SP can upload the content again, proving its availability. The SP has no motivation to proceed with this kind of misbehavior other than putting the customer in a disadvantaged position caused by the lost dispute.}. However, the Filecoin~\cite{protocollabsFilecoinDecentralizedStorage2017}, which works as an incentivization layer on top of IPFS, increases the content availability via economic incentivisation (i.e., punishment in case of lack of proof of storage of the content~\cite{filecoinSlashing}).

The SP uploads the result on both IPFS and Filecoin networks (via Powergate) making the result available even in case of the SP stops serving the result from his node.

@@

\ifx\JOURNAL=IEEE

\appendices
\printbibliography
\else

\section*{Declaration of competing interest}
The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

\section*{Data availability}
No data was used for the research described in the article.

The prototype available at \url{https://anonser.stan.bar}.

The source code available at \url{https://github.com/stanbar/anonymous-provision-of-services-via-blockchain}.

\printbibliography
\appendix
\fi

@@

\begin{itemize}
\item \AgreeablePath
  \begin{itemize}
    \item  \Pos{1}{c}{\normal}{\neutral}, the customer risked his materials but did not pay for the transaction and therefore ends up in a neutral position\footnote{One would argue that the customer has put effort into delivering the materials to the SP or that the materials are valuable. We assume that the materials without personal information are useless, and the effort to deliver the package is negligible.}.
    \item \Pos{1}{s}{\normal}{\neutral}, the SP ends up in a neutral position as she did not spend any resources and the package did not bring her any value.
  \end{itemize}
\item \DisputePath
  \begin{itemize}
    \item \Pos{1}{c}{\dispute}{\minus}, \CustomerLosesBeforePayment{}.
    \item \Pos{1}{s}{\dispute}{\neutral}, \WinForTheSameReason{SP}.
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
\item \AgreeablePath
  \begin{itemize}
    \item \Pos{2}{c}{\abnormal}{\neutral}, the customer remains in the neutral position as he is not obligated to agree with the incorrect $\mathrm{PoD}$.
    \item \Pos{2}{s}{\abnormal}{\neutral}, the SP remains in the neutral position as the package has not brought her any value and she did not spend any resources to provide the service yet.
  \end{itemize}
\item \DisputePath
  \begin{itemize}
    \item \Pos{2}{c}{\abdispute}{\minus}, \CustomerLosesBeforePayment{}, not even to publish correct $\mathrm{PoD}$.
    \item \Pos{2}{s}{\abdispute}{\neutral}, \WinForTheSameReason{SP}.
  \end{itemize}
\end{itemize}

@@

>>>>

\documentclass[pdftex,twocolumn,epjc3]{svjour3} 
\RequirePackage[T1]{fontenc}
\smartqed  % flush right qed marks, e.g. at end of proof
\RequirePackage{graphicx}
\RequirePackage{mathptmx}      % use Times fonts if available on your TeX system
\RequirePackage{flushend}
\RequirePackage[numbers,sort&compress]{natbib}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue,linkcolor=blue]{hyperref}

\journalname{Eur. Phys. J. C}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{float}
\usepackage{etoolbox}

\usepackage{url}
\usepackage{listings}
\usepackage{pdfpages}
\usepackage[english]{babel}
\usepackage{xcolor,colortbl}
\usepackage{scalerel}
\input{constants}

\begin{document}

\title{\TITLE}

\author{\STANLONG\thanksref{e1,addr1}
        \and \JULLONG{}\thanksref{e2,addr1}
        \and \HIGILONG{}\thanksref{e3,addr2}
}

\thankstext{e1}{e-mail: stanislaw.baranski@pg.edu.pl}
\thankstext{e2}{e-mail: julian.szymanski@pg.edu.pl}
\thankstext{e3}{e-mail: hmora@ua.es}

\institute{Department of Electronic, Telecommunication and Informatics, Gdansk University of Technology, Narutowicza 11/12 80-233 Gdansk Poland\label{addr1}
          \and
          Department of Computer Science Technology and Computation, University of Alicante, San Vicente del Raspeig, 03690 Alicante Spain \label{addr2}
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
  \ABSTRACT{}

  \newcommand{\sep}{ \and }
  \keywords{Anonymity\sep{} blockchain\sep{} diagnosis\sep{} e-commerce\sep{} fair-exchange\sep{} privacy\sep{} services}
\end{abstract}

@@

Providing personal information exposes users to privacy risks, i.e. potential loss of control over personal information \cite{smithInformationPrivacyResearch2011}.

Such personal information can be used deliberately or accidentally (e.g., by theft) 
for insider disclosure, unauthorized access, or commercial gains. For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals. 
In turn, it can lead to an unintentional violation of the GDPR or CCPA, profiled advertisements or even criminal activities like identity theft or illegal tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.

@@

The contribution of our paper is:
\begin{itemize}
\item proposing a novel protocol that:
  \begin{itemize}
  \item allows \textbf{anonymous} service provision, i.e., the service provider does not need to collect any personal information from the customer.
  \item achieves \textbf{fairness} by carefully designing the protocol as an interactive non-cooperative game, in which the SP remains in an advantageous position and the customer in a disadvantageous position with an option to start a dispute in case a misbehaviour of SP.
  \item \textbf{does not rely on centralized TTP}, but uses decentralized blockchain and distributed content-addressable storage network.
  \item In conflict-free transactions does not require customers to interact with the blockchain, achieving better \textbf{user-experience and practicality}.
  \item allows the \textbf{delivery of physical materials}, which was rarely addressed by other researchers or based on strong and unpractical assumptions.
  \item guarantees the \textbf{remote availability of the results}, even in case of the SP denial of service.
  \end{itemize} 
\item Systematise often misused definitions of anonymity, pseudonymity, linkability, and traceability.
\item Proposing a framework for analyzing fairness in fair-exchange protocols.
\item Discuss the possible improvements to the protocol with the use of secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution techniques.
\end{itemize}

@@

To our best knowledge, the first system that allowed for fair exchange of physical products was proposed by Zhang et al. in 2006~\cite{zhangPracticalFairExchangeEPayment2006}. The protocol uses buyer's bank as TTP, and assumes no coalition between parties to achieve anonymity.

Authors of~\cite{mohammedalarajFairnessPhysicalProducts2012} proposed an protocol for fair-exchange involving physical materials delivery. The protocol assumes the existence of an offline~\footnote{\textit{Offline} (also called \textit{optimistic}) TTP compared to \textit{online} TTP is in improvement which assumes the TTP being involved only in the case of a dispute between parties~\cite{rayFairExchangeEcommerce2002}.} TTP that is involved only in the event of a dispute. The protocol works as follows: 
\begin{enumerate}
\item The buyer sends an encrypted payment to the seller along with the proof of validity.
\item The seller validates the proof, which convinces him that the decrypted payment will also be valid.
\item The seller forwards the physical product to the trusted delivery agent (DA).
\item The buyer verifies whether the product is the one he ordered.
\item The buyer creates a proof of delivery and sends it along with the decryption key to the seller.
\end{enumerate}

@@

\begin{enumerate}
    \item The buyer buys a digital coin from his bank. Blind signature is used to preserve privacy.
    \item The buyer sends to the seller the purchase details, address of DC, customer's bank signature, and some meta data to preserve the integrity of transaction, communication is done over Tor.
    \item The seller request a redemption of the digital coin.
    \item The seller posts the product to the DC via delivery serivice.
    \item The DA collects the product from the seller's cabinet and posts it to the DC.
    \item The buyer collects the product from the DC using a password.
    \item The buyer checks if the product is the ordered one, if not, opens a dispute to TTP.
\end{enumerate}

@@

The protocol works as follows:
\begin{enumerate}
    \item Alice and Bob generate a 2-of-2 threshold escrow account using Thresh-Key-Gen protocol and send funds to it.
    \item Alice and Bob split their secret keys into \(n=2t+1\) secret shares using Shamir Secret Sharing protocol, where \(n\) is the number of mediators that participate in the decentralized network and \(t+1\) becomes the threshold of a sufficient number of mediators to reconstruct the secret key.
    \item Alice and Bob encrypt each \textit{i}-th key share using public key of \textit{i}-th mediator.
    \item Alice and Bob exchange the sets of encrypted key shares with each other and send funds to the escrow account.
\end{enumerate}

@@

Meng et al., 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol by the crowd-sourced dispute resolution system. However, it does not take anonymity into consideration.

Bîrjoveanu, 2022~\cite{birjoveanuTwoPartyECommerceProtocols2022} is the closest to our protocol, however, it is based on strong assumptions, namely, existence of TTP, banks supporting confidential transactions with commit buffers, and maintaining a global list of coins' serial numbers.

@@

{\begin{table*}
\centering
\newcommand{\YES}{\cellcolor{green!50}Yes}
\newcommand{\YESBUT}{\cellcolor{green!25}Yes*}
\newcommand{\ID}{\cellcolor{green!25}Identity}
\newcommand{\PSEUDO}{\cellcolor{green!35}Pseudonym}
\newcommand{\ANON}{\cellcolor{green!50}Anonymity}
\newcommand{\NO}{\cellcolor{red!50}No}
\newcommand{\TTP}{\cellcolor{red!50}TTP}
\newcommand{\BC}{\cellcolor{green!50}BC}
\caption{Comparision of related works.}
\label{tab:comparision}
\setlength{\tabcolsep}{3pt}

\begin{tabular}{cccccc}

\noalign{\smallskip}\hline\noalign{\smallskip}
Protocol & Fair exchange & Anonymity & Dispute resolution & Trust & Physical delivery \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\cite{zhangPracticalFairExchangeEPayment2006} (2006) & \YES & \YESBUT & \YES & \TTP & \YES \\
\cite{mohammedalarajFairnessPhysicalProducts2012} (2012) & \YESBUT & \NO & \YES & \TTP & \YES \\
Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} (2017) & \YES & \PSEUDO & \NO & \BC & \YES \\
\cite{hinarejosSolutionSecureCertified2019} (2019) & \YES & \NO & \NO & \BC & \NO \\
Themis~\cite{mengThemisDecentralizedEscrow2019} (2019) & \YES & \NO & \YES & \BC & \NO \\
PPPDCP~\cite{birjoveanuTwoPartyECommerceProtocols2022} (2022) & \YES & \YES & \YES & \TTP & \YES \\
This paper & \YES & \YES & \YES & \BC & \YES \\
\noalign{\smallskip}\hline

@@

\end{table*}

@@

\subsection{Physical products}\label{sec:physical-products}
The use cases we address in this paper use physical materials like blood, urine, hair, and other biological materials.
This requirement, combined with the requirement of anonymity, is a challenging part of the fair-exchange protocols. The problem arises when the seller wants to sent the product to the buyer who wants to remain anonymous. Most of the existing protocols either assume the existence of trusted delivery agent~\cite{mohammedalarajFairnessPhysicalProducts2012,birjoveanuAnonymityFairexchangeEcommerce2015}, or use complex delivery mechanism similar to onion routing involving multiple many delivery services~\cite{altawyLelantosBlockchainBasedAnonymous2017}.

However, our use case is different in that the physical materials are transferred from the (anonymous) customer to the (public) SP. This, allows for simplification of the delivery process. We assume that there is a way to anonymously deliver a package without revealing the customer personal information either via SP's drop box, Parcel Locker services (e.g. Amazon Locker, InPost~\cite{inpostParcelLockerService}), a customer's trusted party, of even post office.

@@

\begin{figure}[h!]
\includegraphics[width=\linewidth]{anonymity-diagram.png}
\centering
\caption{Let us assume Alice to be the customer willing to keep her identity anonymous and Bob to be the public SP. Alice controls two addresses, 1 and 2; the connection between her real identity and the first address has been compromised, and therefore the identification is possible; the connection between the second pseudonym is still unknown and therefore anonymous. Alice takes two actions; the first one from the compromised address and the second one from the anonymous one. The first action is confidential; therefore, even though the pseudonym has been compromised, the action can not be associated with Alice. The second action is transparent; therefore, Alice maintains her anonymity as long as the connection to the second pseudonym is concealed.}

@@

\item $\mathrm{T}_\mathrm{issue}$ - time at which the $\mathrm{PoD}$ is issued by the SP.
\item
  $\mathrm{T}_\mathrm{pay}$ - deadline to pay for the transaction.
\item
  $\mathrm{T}_\mathrm{provide}$ - deadline to provide the result of the service, i.e. publish $\mathrm{PoP}$.
\item $\mathrm{address}$ - payment address of the SP's anonymous blockchain account.
\item $\mathrm{provisionID}$ - the number uniquely identifying the transaction previously generated by the customer.
\item $\mathrm{pk(C)}$ - customer's public key used to encrypt the result published on the public storage network.
\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature guaranteeing non-repudiation.
\end{itemize}

@@

\begin{figure}[ht!]
\includegraphics[width=\linewidth]{anonser-protocol.png}
\centering
\caption{Messages exchanged in the protocol. Solid arrows indicate requests and dashed arrows indicate responses.}
\label{fig:protocol-diagram}
\end{figure}

@@

\begin{enumerate}
\item Both parties start from a neutral position $\neutral$.
\item After completing a transaction, both parties end up in advantaged positions (\plus{}). In other words, they have an intrinsic motivation to initialize and complete the transaction.
\item The protocol steps are atomic—there are no intermediate steps.
\item The protocol can go only forward—there is no way of reverting any action.
\item Repeating the first step starts a new transaction. Repeating any other step is considered abnormal and gets ignored. For example, paying for the invoice twice does not cause any effect on the curse of the protocol.
\item Once published, the result is available to the customer on the storage network. The idea of guaranteeing it cryptographically is discussed in Section~\ref{sec:discussion}.
\item Winning the dispute leads to a neutral position ($\neutral$).
\item Losing the dispute leads to a punishment greater than any reward, leading to a disadvantaged position (\minus{}). Hence, the rational customer will not start a dispute that he is unsure of winning.
\item Both the customer and the SP are rational (selfish). They always prefer to go from the worst position (\minus{} or $\neutral${}) to a better position ($\neutral$ or \plus), but also risk a temporary worst position in favor of a later better position if and only if at any time they can get out of the worst position; in particular, at any time the customer can start a dispute and, if the SP has misbehaved, get out of disadvantaged position (\minus) to the neutral position ($\neutral$).
\item We assume that the Customer's materials without personal information are useless, and the effort to deliver the package is negligible, so that the Customer's first step does not lead to disadvantaged position.
\item We assume the processing cost of publishing $\mathrm{PoD}$ is negligible and balance out the effort of delivering the package by the Customer.
\end{enumerate}

@@

\begin{figure}[h!]
\includegraphics[width=\linewidth]{model.png}
\centering
\caption{Positions after each step of protocol}
\label{fig:positions}
\end{figure}

@@

The Figure~\ref{fig:misbehaviour} shows the transitions of positions when the SP tries to misbehave and does not execute service, and so does not publish $\mathrm{PoP}$ after receiving the payment. After the deadline $\mathrm{T}_\mathrm{provide}$ the SP can not publish valid $\mathrm{PoP}$ and so the Customer starts a dispute. The Customer wins the dispute as the SP is unable to proof the $\mathrm{PoP}$ was published before $\mathrm{T}_\mathrm{provide}$. The protocol ends up neutral to the customer and disadvantaged to the SP positions.

\begin{figure}[h!]
\includegraphics[width=\linewidth]{misbehaviour.png}
\centering
\caption{Transitions of positions where the SP is misbehaving and the customer starts a dispute}
\label{fig:misbehaviour}
\end{figure}
the rational path for both parties is to follow the protocol as shown in the Figure~\ref{fig:rational}.

\begin{figure}[h!]
\includegraphics[width=\linewidth]{rational.png}
\centering
\caption{Transitions of positions where both the customer and the SP are following the protocol}
\label{fig:rational}
\end{figure}

@@

\paragraph{Provable Results Availability}
Content addressable networks such as IPFS can not guarantee the availability of the content\footnote{Nothing prevents the SP from publishing the result, receiving the $\mathrm{cid}$, publishing $\mathrm{PoP}$, and immediately after removing the result from the local storage. In case of dispute, the SP can upload the content again, proving its availability. The SP has no motivation to proceed with this kind of misbehavior other than putting the customer in a disadvantaged position caused by the lost dispute.}. However, the Filecoin~\cite{protocollabsFilecoinDecentralizedStorage2017}, which works as an incentivization layer on top of IPFS, increases the content availability via economic incentivisation (i.e., punishment in case of lack of proof of storage of the content~\cite{filecoinSlashing}). Compared to typical blockchain networks, Filecoin focuses on data storage and thus makes it cheaper than storing it on blockchains like Bitcoin or Ethereum.

The SP uploads the result on both IPFS and Filecoin networks (via Powergate) making the result free in case of normal behaviour, and highly-available in case of the SP stops serving the result from his node.

@@

\appendix

@@

\begin{itemize}
\item \AgreeablePath
  \begin{itemize}
    \item  \Pos{1}{c}{\normal}{\neutral}, the customer risked his materials but did not pay for the transaction and therefore ends up in a neutral position (see Assumption 10. in Section \ref{sec:assumptions}).
    \item \Pos{1}{s}{\normal}{\neutral}, the SP ends up in a neutral position as she did not spend any resources and the package did not bring her any value.
  \end{itemize}
\item \DisputePath
  \begin{itemize}
    \item \Pos{1}{c}{\dispute}{\minus}, \CustomerLosesBeforePayment{}.
    \item \Pos{1}{s}{\dispute}{\neutral}, \WinForTheSameReason{SP}.
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
\item \AgreeablePath
  \begin{itemize}
    \item \Pos{2}{c}{\abnormal}{\neutral}, the customer remains in the neutral position as he is not obligated\footnote{By not obligated we understand the situation where a party does not risk any resources by not taking the action} to agree with the incorrect $\mathrm{PoD}$.
    \item \Pos{2}{s}{\abnormal}{\neutral}, the SP remains in the neutral position as the package has not brought her any value and she did not spend any resources to provide the service yet.
  \end{itemize}
\item \DisputePath
  \begin{itemize}
    \item \Pos{2}{c}{\abdispute}{\minus}, \CustomerLosesBeforePayment{}, not even to publish correct $\mathrm{PoD}$.
    \item \Pos{2}{s}{\abdispute}{\neutral}, \WinForTheSameReason{SP}.
  \end{itemize}
\end{itemize}

@@

\bibliographystyle{spbasic}
\bibliography{bibliography}

\end{document}
